### 2019-05-16 thesis.tex
Still editing the introduction

In the context of physics, the word ``plasma'' is used to designate a gas whose
degree of ionization is such that the forces of electric and magnetic nature of
the charged particles overcome the influence of the collisions between neutral
particles, in the overall dynamics of the gas. Besides that, the

>>>>

% degree of ionization is such that the interactions involving forces of electric
% and magnetic nature of the charged particles, overcome the influence of the
% collisions between neutral particles, in the overall dynamics of the gas.
In the context of physics, the word "plasma" designates a gas whose degree of
ionization is such that the interactions involving forces of electric and magnetic
nature, of the charged particles, overcome the influence of the binary collisions
between neutral particles on the overall dynamics of the gas. The charged particles
might also interact with the neutral components of the gas
